Coalition Formation Algorithm of Prosumers in a Smart Grid Environment

### 2015-02-17 Article.tex
last

However, we will see in the following, that a clique (a complete subgraph) in our filtered decorelation-based graph exhibit, by construction, low correlation. We indeed removed in the filtering (see $\epsilon$-graphs) all links that stand for high correlation. There exists greedy heuristics based on cliques in the litterature such as clique percolation, \cite{Lancichinetti} which realizes local optimizations of a fitness function and results in overlapping community structures.

@@

$ \rho_{ij} $ is the Pearson correlation coefficient between $ P_{i} $ and $ P_{j} $ (see table \ref{table1} for notations). Because all distributions are gaussians, we can easily write the probability $ Pr[P_{ij} \leq P_{ij}^{CRCT} ] $ as :

@@

\subsection{Utility function}\label{subsec:UtilityFunc}
As solving the optimization problem (see eq. \ref{problem}) is considered NP-hard, we address this problem with a heuristic based on a utility function (eq. \ref{utility}) that derives directly from the problem constraints. That is, if a coalition cannot provide a valid contract value, it receives a utility of zero. Furthermore, the utility increases with the overall production (sum of the contracted values) as stated in the objective of eq.\ref{problem}. The stability of the coalitions is also present in this utility function through the $ \phi $ parameter. Finally, the $ 1/|s|^{\alpha} $ term in eq. \ref{utility} controls the sizes of the coalitions (for simplicity, in the rest of the paper $ \alpha $ is set to one).

@@

However, these clusters of strongly correlated time-series are the exact opposite of what we are seeking. We can indeed consider them directly as coalitions and compute their utilities, and the results show (see the green curves with diamonds on figure \ref{Fig4}), as expected, terrible values. We will indeed consider in section \ref{sec:results} this case as a worst case scenario, far worse than a trivial random split of the agents in the same number of coalitions (see the red curves with triangles of the random case on figure \ref{Fig4}).

@@

In figure \ref{Fig2}b, we fix the reliability to a given empirical value ($\phi = 0.08 $). We can observe how the social welfare $\sum_{s \in S} \mathcal{U}_{\phi,\ P^{MIN}}(s)$ evolves according to $P^{MIN}$ and $ N_{COAL} $. In our setting we notice a maximum point around $ N_{COAL} = 3 $, followed by a decrease. There is clearly a maximum number of coalitions sustainable for a given set of parameters. After that value the coalitions newly formed won't be able to pass the grid requirements. Moreover, reckon that increasing $ N_{COAL} $ means also increasing $ \epsilon $, leading to denser graphs, meaning that the algorithm performance will also decrease.

>>>>

However, we will see in the following, that a clique (a complete subgraph) in our filtered decorelation-based graph exhibits, by construction, low correlation. We indeed removed in the filtering (see $\epsilon$-graphs) all links that stand for high correlation. There exists greedy heuristics based on cliques in the litterature such as clique percolation, \cite{Lancichinetti} which realizes local optimizations of a fitness function and results in overlapping community structures.

@@

$ \rho_{ij} $ is the Pearson correlation coefficient between $ P_{i} $ and $ P_{j} $ (see table \ref{table1} for notations). Because all distributions are gaussians in this example, we can easily write the probability $ Pr[P_{ij} \leq P_{ij}^{CRCT} ] $ as :

@@

\subsection{Utility function}\label{subsec:UtilityFunc}
As solving directly the optimization problem (see eq. \ref{problem}) is considered NP-hard, we address this problem with a heuristic based on a utility function (eq. \ref{utility}) that derives directly from the problem constraints. That is, if a coalition cannot provide a valid contract value, it receives a utility of zero. Furthermore, the utility increases with the overall production (sum of the contracted values) as stated in the objective of eq.\ref{problem}. The stability of the coalitions is also present in this utility function through the $ \phi $ parameter. Finally, the $ 1/|s|^{\alpha} $ term in eq. \ref{utility} controls the sizes of the coalitions (for simplicity, in the rest of the paper $ \alpha $ is set to one).

@@

However, these clusters of strongly correlated time-series are the exact opposite of what we are seeking. We can indeed consider them directly as coalitions and compute their utilities, and the results show (see the green curves with diamonds on figure \ref{Fig4}), as expected, terrible values. We will indeed consider in section \ref{sec:results} this case as a \textit{"worst case scenario"}, far worse than a trivial random search (see the red curves with triangles of the random case on figure \ref{Fig4}).

@@

In figure \ref{Fig2}b, we fix the reliability to a given empirical value ($\phi = 0.08 $). We can observe how the social welfare $\sum_{s \in S} \mathcal{U}_{\phi,\ P^{MIN}}(s)$ evolves according to $P^{MIN}$ and $ N_{COAL} $. In our setting we notice a maximum point around $ N_{COAL} = 3 $, followed by a decrease. There is clearly a maximum number of coalitions sustainable for a given set of parameters. After that value the coalitions newly formed won't be able to pass the grid requirements. Moreover, reckon that increasing $ N_{COAL} $ means also increasing $ \epsilon $, leading to denser graphs and a decrease of the algorithm's performances.
